\subsubsection{Extract configurations based on frames' properties}
\index[action]{Extract configurations based on frames' properties}
\index[command]{--extract +conf}

This action extracts frames based on properties read from a file.

\hdashrule[0.5ex][x]{\textwidth}{1pt}{3mm}

\begin{itemize}
\item[Command:] \emph{--framesByProperty}

\vspace{0.5cm}
\item[List of flags:] 
\emph{+f [conf.xyz]}\\
  defines the file that contains the properties used to select the frames to be written out.

\emph{+out [cluster.xyz]}\\
  defines the root of the output file name.
  The output is currently only in XYZ format and one file is created for each frame processed.

\emph{+min [list]}\\
  comma separated list of the minimum values of each property to be written out.
  INF or * can be used to accept any values of a property.

\emph{+max [list]}\\
  comma separated list of the maximum values of each property to be written out.
  INF or * can be used to accept any values of a property.

\emph{+out [list]}\\
  comma separated list of the maximum values of each property to be written out .
  INF or * can be used to accept any values of a property.

\vspace{0.5cm}  
\item[Examples:]
\begin{small}
\begin{Verbatim}[frame=single]
gpta.x --i coord.pdb --framesByProperty +f colvar_gpta +out out.1.dcd \\
   +min *,1.15,-1.0,0.0 +max *,1.30,-0.9,0.2
\end{Verbatim}
\end{small}

\vspace{0.5cm} 
\item[Screen output:]
\begin{scriptsize}
\begin{verbatim}
...
__________________________________________________________________________________________________________
Extract frames by properties
...Properties file..................................: colvar_gpta
...Number of properties in file.....................:           4
......Limits for property #1........................:    999.0000       0.256010E+08
......Limits for property #2........................:      1.1500         1.3000
......Limits for property #3........................:     -1.0000        -0.9000
......Limits for property #4........................:      0.0000         0.2000
...Output file......................................: out.1.dcd
__________________________________________________________________________________________________________...
\end{verbatim}
\end{scriptsize}

%\vspace{0.5cm}
%\item[File output:]
%\begin{scriptsize}
%\begin{verbatim}
%...
%\end{verbatim}
%\end{scriptsize}

\end{itemize}

\hdashrule{\textwidth}{1pt}{}
