\subsubsection{Density Profile (1D)}
\index[action]{Density Profile (1D)}
\index[command]{--dmap1D}

This action computes the 1D density profile along one of the crystallographic directions.
The density profile can be computed for a subset of atoms that can be selected either by their label (\emph{+s}), their indices (\emph{+i}) or by the molecule they belong to (\emph{+mol}). Mixed selections, \emph{e.g.} based on labels and indices, are not allowed within one command. The command can be repeated.

\hdashrule[0.5ex][x]{\textwidth}{1pt}{3mm}

\begin{itemize}
\item[Command:] \emph{--dmap1D}

\vspace{0.5cm}
\item[List of flags:] 
\emph{+out [dmap1D.out]}\\
  defines the output file name.

\emph{+s [species]} or \emph{+i [indices]} or \emph{+mol [molecule name]}\\
  select the species to be used in the calculation using the atoms' names or their indices or the name of the molecules they belong to.
  The species selection is done by providing a comma separated list of atom names.
  The index selection can be done by providing a comma separated list of indices or in loop format B:E:(S), where the stride is optional.
  The \emph{+mol} flag requires \emph{--top} flag, and the molecules are seleceted using the names given to them by the \emph{--top} command.

\emph{+x}\\
  sets the $x$ direction for the calculation of the 1D density profile.

\emph{+y}\\
  sets the $y$ direction for the calculation of the 1D density profile.

\emph{+z}\\
  sets the $z$ direction for the calculation of the 1D density profile.

\emph{+nbin [100]}\\
  defines the number of bins for the 1D density profile.

\vspace{0.5cm}  
\item[Examples:]
\begin{small}
\begin{Verbatim}[frame=single]
gpta.x --i coord.pdb --dmap1D +x +s O 
gpta.x --i coord.pdb --dmap1D +z +s O +out dmap.out
gpta.x --i coord.pdb --dmap1D +z +s Ca +nbin 200 +out dmap.out
gpta.x --i coord.pdb --dmap1D +z +i 1:300:3 +out dmap.out
\end{Verbatim}
\end{small}

\vspace{0.5cm} 
\item[Screen output:]
\begin{scriptsize}
\begin{verbatim}
...
_________________________________________________________________________________________________________
Computing 1D density profile
...Output file.....................................: dmap.out
...Atoms selection for --dmap1D
......Selection command............................:
......Atoms selected in the first group............:         520
_________________________________________________________________________________________________________
...
\end{verbatim}
\end{scriptsize}

\vspace{0.5cm}
\item[File output:]
\begin{scriptsize}
\begin{verbatim}
# Position  | Density [atom/angstrom^3]
    0.4320800000E+00     0.1376089546E-01
    0.1296240000E+01     0.4867850937E-02
...
\end{verbatim}
\end{scriptsize}

\end{itemize}

\hdashrule{\textwidth}{1pt}{}
